---
title: "EDA on Text"
author: "Chirag Ahluwalia"
date: "4/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Descriptive Statistics 

```{r}
library(readxl)
#ratemdsfinal <- read_excel("ratemdsfinal.xlsx")
ratemdsfinal=read_xlsx('C:/Users/rramn/Documents/Healthcare_analytics/physician_reviews_mining/Reviews/ratemdsfinal.xlsx')
library(dplyr)
library(kableExtra)
library(xtable)
library(stargazer)
library(knitr)
library(psych)
library(ggplot2)
colSums(is.na(ratemdsfinal))

ratemdsfinal$`Years of Experience`[is.na(ratemdsfinal$`Years of Experience`)]=round(mean(ratemdsfinal$`Years of Experience`,na.rm = T))

# ghetting only the numeric columsn 
num_cols <- unlist(lapply(ratemdsfinal, is.numeric))  
rate <- ratemdsfinal[, num_cols]

rate$...1<- NULL
str(rate)
names(rate)[1]<- "Exp"

# Print Descriptive Statistics for RateMDs
kable(xtable(describe(rate)[c(3,4,5,8,9,11)]))


# Checking for Normality 
#library(ggpubr)
#ggqqplot(rate$Rating)
#shapiro.test(rate$Rating)

#ggqqplot(rate$Positive_Proportion)
#shapiro.test(rate$Positive_Proportion)

#ggqqplot(rate$Negative_Proportion)
#shapiro.test(rate$Negative_Proportion)

#ggqqplot(rate$`Average pos_score`)
#shapiro.test(rate$`Average pos_score`)

#ggqqplot(rate$`Average neg_score`)
#shapiro.test(rate$`Average neg_score`)


## Multiple t-tests for RateMDs
a<- lapply(rate, function(x) t.test(x ~ ratemdsfinal$Gender, var.equal = TRUE)$p.value)
# T-Test for RateMDs with Gender 
print(a)
```
## Statistics based on Gender  

```{r}

#str(ratemdsfinal)
ratemdsfinal$Gender<- factor(ratemdsfinal$Gender)

rate %>% #plot rating over Gender 
  ggplot(aes(x=Rating,fill=ratemdsfinal$Gender))+
  geom_density(alpha=.4,position="identity")+
  labs(title = "Density of Rating by Gender on RateMDs\n(blue=Female, red=Male)",x="Rating",y = "Density of Rating")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

rate %>% #plot Positive_Proportion over Gender 
  ggplot(aes(x=Positive_Proportion,fill=ratemdsfinal$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Positive Proportion by Gender on RateMDs\n(blue=Female, red=Male)",x="Positive_Proportion",y = "Density of Positive Proportion")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

rate %>% #plot Negative_Proportion over Gender 
  ggplot(aes(x=Negative_Proportion,fill=ratemdsfinal$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Negative_Proportion by Gender on RateMDs\n(blue=Female, red=Male)",x="Negative_Proportion",y = "Density of Negative_Proportion")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

rate %>% #plot `Average neg_score` over Gender 
  ggplot(aes(x=`Average neg_score`,fill=ratemdsfinal$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of `Average neg_score` by Gender on RateMDs\n(blue=Female, red=Male)",x="`Average neg_score`",y = "Density of `Average neg_score`")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

rate %>% #plot `Average pos_score` over Gender 
  ggplot(aes(x=`Average pos_score`,fill=ratemdsfinal$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of `Average pos_score` by Gender on RateMDs\n(blue=Female, red=Male)",x="`Average pos_score`",y = "Density of `Average pos_score`")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

ratemdsfinal %>% #plot Years of Experience over Gender 
  ggplot(aes(x=`Years of Experience`,fill=ratemdsfinal$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Years of Experience by Gender on RateMDs\n(blue=Female, red=Male)",x="Years of Experience - in years",y = "Density of Years of Experience")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

rate %>% #plot Overall_score over Gender 
  ggplot(aes(x=Overall_score,fill=ratemdsfinal$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Overall_score by Gender on RateMDs\n(blue=Female, red=Male)",x="Overall_score",y = "Density of Overall_score")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

```
## Statistics by No of Years of Experience 

```{r}
summary(ratemdsfinal$`Years of Experience`)

ratemdsfinal$`Years of Experience` <- as.factor(ratemdsfinal$`Years of Experience`)
levels(ratemdsfinal$`Years of Experience`) = list("Less than 10 years" = c(0:10),
                                       "11 to 20 years" =c(11:20),
                                       "21 to 30 years " = c(21:30), 
                                       "31 years and above" = c(31:56))
summary(ratemdsfinal$`Years of Experience`)

boxplot(ratemdsfinal$Rating~ratemdsfinal$`Years of Experience`, # Specify the variables to graph, quantitative variable first
        col=c("orange","thistle","lightgreen","lightblue","gray","yellow"), # Specify the data set that contains the variables
        main = "Rating over Years of Experience on RateMDs", #Create the chart title
        xlab = "Rating",  #Create the x-axis label
        ylab = "",
        las=1,  # Width of box as proportion of original
        whisklty = 1,  # Whisker line type; 1 = solid line
        staplelty = 0,  # Staple (line at end) type; 0 = none
        outpch = 16,  # Symbols for outliers; 16 = filled circle
        outcol = "slategray3", 
        notch=T,horizontal = T# Color for outliers
) #Create the y-axis label

# Checking the Significance Level of the Factors created
years.aov1 <- aov(ratemdsfinal$Rating~ratemdsfinal$`Years of Experience`, data = ratemdsfinal)
summary(years.aov1)
 
TukeyHSD(years.aov1)

# Thus, there is not much significance 

```

## Plots based on Years of Experience over Dependent Variables 

```{r}

boxplot(ratemdsfinal$Rating~ratemdsfinal$`Years of Experience`, # Specify the variables to graph, quantitative variable first
        col=c("orange","thistle","lightgreen","lightblue","gray","yellow"), # Specify the data set that contains the variables
        main = "Rating over Years of Experience on RateMDs", #Create the chart title
        xlab = "Rating",  #Create the x-axis label
        ylab = "Years of Experience",
        las=1,  # Width of box as proportion of original
        whisklty = 1,  # Whisker line type; 1 = solid line
        staplelty = 0,  # Staple (line at end) type; 0 = none
        outpch = 16,  # Symbols for outliers; 16 = filled circle
        outcol = "slategray3", 
        notch=T,horizontal = T# Color for outliers
) #Create the y-axis label

rate %>% #plot rating over Gender 
  ggplot(aes(x=Rating,fill=ratemdsfinal$Gender))+
  geom_density(alpha=.4,position="identity")+
  labs(title = "Density of Rating over Gender spread across Years of Experience on RateMDs\n(blue=Female, red=Male)",x="Rating",y = "Density of Rating")+#add title and axis labels
  theme(legend.position="none")+#hide the side signal of fill parameter
 facet_wrap(ratemdsfinal$`Years of Experience`)

```

## Healthgrades

```{r}

library(readxl)
#healthgrades <- read_excel("healthgradesfinal.xlsx")
healthgrades=read_xlsx('C:/Users/rramn/Documents/Healthcare_analytics/physician_reviews_mining/Reviews/healthgradesfinal.xlsx')
str(healthgrades)

healthgrades$Gender<- factor(healthgrades$Gender)

colSums(is.na(healthgrades))

healthgrades$`Years of Experience`[is.na(healthgrades$`Years of Experience`)]=round(mean(healthgrades$`Years of Experience`,na.rm = T))

# ghetting only the numeric columsn 
num_cols <- unlist(lapply(healthgrades, is.numeric))  
health <- healthgrades[, num_cols]

# Print Descriptive Statistics for RateMDs
kable(xtable(describe(health)[c(3,4,5,8,9,11)]))


## Multiple t-tests for RateMDs
a<- lapply(health[], function(x) t.test(x ~ healthgrades$Gender, var.equal = TRUE)$p.value)
print(a)

```

## Statistics based on Gender 

```{r}

## Plots with Gender 
health %>% #plot rating over Gender 
  ggplot(aes(x=Rating,fill=healthgrades$Gender))+
  geom_density(alpha=.4,position="identity")+
  labs(title = "Density of Rating by Gender on HealthGrades\n(blue=Female, red=Male)",x="Rating",y = "Density of Rating")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

health %>% #plot Positive_Proportion over Gender 
  ggplot(aes(x=Positive_Proportion,fill=healthgrades$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Positive Proportion by Gender on HealthGrades\n(blue=Female, red=Male)",x="Positive_Proportion",y = "Density of Positive Proportion")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

health  %>% #plot Negative_Proportion over Gender 
  ggplot(aes(x=Negative_Proportion,fill=healthgrades$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Negative_Proportion by Gender on HealthGrades\n(blue=Female, red=Male)",x="Negative_Proportion",y = "Density of Negative_Proportion")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

health  %>% #plot `Average neg_score` over Gender 
  ggplot(aes(x=`Average neg_score`,fill=healthgrades$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of `Average neg_score` by Gender on HealthGrades\n(blue=Female, red=Male)",x="`Average neg_score`",y = "Density of `Average neg_score`")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

health %>% #plot `Average pos_score` over Gender 
  ggplot(aes(x=`Average pos_score`,fill=healthgrades$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of `Average pos_score` by Gender on HealthGrades\n(blue=Female, red=Male)",x="`Average pos_score`",y = "Density of `Average pos_score`")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

health  %>% #plot Years of Experience over Gender 
  ggplot(aes(x=`Years of Experience`,fill=healthgrades$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Years of Experience by Gender on HealthGrades\n(blue=Female, red=Male)",x="Years of Experience - in years",y = "Density of Years of Experience")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

health %>% #plot Overall_score over Gender 
  ggplot(aes(x=Overall_score,fill=healthgrades$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Overall_score by Gender on HealthGrades\n(blue=Female, red=Male)",x="Overall_score",y = "Density of Overall_score")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

```

## Statistics based on Years of Experience in HealthGrades 

```{r}

summary(healthgrades$`Years of Experience`)

healthgrades$`Years of Experience` <- as.factor(healthgrades$`Years of Experience`)
levels(healthgrades$`Years of Experience`) = list("Less than 10 years" = c(0:10),
                                       "11 to 20 years" =c(11:20),
                                       "21 to 30 years " = c(21:30), 
                                       "31 years and above" = c(31:56))
summary(healthgrades$`Years of Experience`)

boxplot(healthgrades$Rating~healthgrades$`Years of Experience`, # Specify the variables to graph, quantitative variable first
        col=c("orange","thistle","lightgreen","lightblue","gray","yellow"), # Specify the data set that contains the variables
        main = "Rating over Years of Experience on Healthgrades", #Create the chart title
        xlab = "Rating",  #Create the x-axis label
        ylab = "Years of Experience",
        las=1,  # Width of box as proportion of original
        whisklty = 1,  # Whisker line type; 1 = solid line
        staplelty = 0,  # Staple (line at end) type; 0 = none
        outpch = 16,  # Symbols for outliers; 16 = filled circle
        outcol = "slategray3", 
        notch=T,horizontal = T# Color for outliers
) #Create the y-axis label

# Checking the Significance Level of the Factors created
years.aov1 <- aov(healthgrades$Rating~healthgrades$`Years of Experience`, data = healthgrades)
summary(years.aov1)

TukeyHSD(years.aov1)

# Thus, there is not much significance 

```

## Plots for Years of Experience on HealthGrades 

```{r}

health %>% #plot rating over Gender 
  ggplot(aes(x=Rating,fill=healthgrades$Gender))+
  geom_density(alpha=.4,position="identity")+
  labs(title = "Density of Rating over Gender spread across Years of Experience on HealthGrades\n(blue=Female, red=Male)",x="Rating",y = "Density of Rating")+#add title and axis labels
  theme(legend.position="none")+#hide the side signal of fill parameter
 facet_wrap(~healthgrades$`Years of Experience`)

```


## Combined 

```{r}
options(scipen=999)
#Combined(Both Ratemds and Healthgrades)

hcommon=data.frame(healthgrades[,c(3,5,20,21,22,23,24,25,26,27,28,29,30,31,32,7,14,17,16,19,33)])

rcommon=data.frame(ratemdsfinal[,c(3,4,17,18,19,20,21,22,23,24,25,26,27,28,32,6,11,14,12,16,33)])

dcombine=data.frame(rbind(hcommon,rcommon))
str(dcombine)

# Print Descriptive Statistics for Combined
kable(xtable(describe(dcombine)[c(3,4,5,8,9,11)]))
## Multiple t-tests for RateMDs
a<- lapply(dcombine[,-c(1:2)], function(x) t.test(x ~ dcombine$Gender, var.equal = TRUE)$p.value)
print(a)

# Checking the Significance Level of the Gender 
years.aov1 <- aov(dcombine$Rating~dcombine$Gender, data = dcombine)
summary(years.aov1)
 
TukeyHSD(years.aov1)

# Thus, there is not much significance 

# Checking the Significance Level of the Years of Experience  
years.aov1 <- aov(dcombine$Rating~dcombine$Years.of.Experience, data = dcombine)
summary(years.aov1)
 
TukeyHSD(years.aov1)

# Thus, there is not much significance

```

## Plotting for Combined results 

```{r}

dcombine %>% #plot rating over Gender 
  ggplot(aes(x=Rating,fill=Gender))+
  geom_density(alpha=.4,position="identity")+
  labs(title = "Density of Rating by Gender on Both - Healthgrades and RateMDs\n(blue=Female, red=Male)",x="Rating",y = "Density of Rating")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

dcombine %>% #plot Positive_Proportion over Gender 
  ggplot(aes(x=Positive_Proportion,fill=dcombine$Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Positive Proportion by Gender on Both - Healthgrades and RateMDs\n(blue=Female, red=Male)",x="Positive_Proportion",y = "Density of Positive Proportion")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

dcombine %>% #plot Negative_Proportion over Gender 
  ggplot(aes(x=Negative_Proportion,fill=Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Negative_Proportion by Gender on Both - Healthgrades and RateMDs\n(blue=Female, red=Male)",x="Negative_Proportion",y = "Density of Negative_Proportion")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

dcombine %>% #plot `Average neg_score` over Gender 
  ggplot(aes(x=Average.neg_score,fill=Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of `Average neg_score` by Gender on Both - Healthgrades and RateMDs\n(blue=Female, red=Male)",x="`Average neg_score`",y = "Density of `Average neg_score`")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

dcombine %>% #plot `Average pos_score` over Gender 
  ggplot(aes(x=Average.pos_score,fill=Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of `Average pos_score` by Gender on Both - Healthgrades and RateMDs\n(blue=Female, red=Male)",x="`Average pos_score`",y = "Density of `Average pos_score`")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter

dcombine %>% #plot Overall_score over Gender 
  ggplot(aes(x=Overall_score,fill=Gender))+
  geom_density(alpha=.5,position="identity")+
  labs(title = "Density of Overall_score by Gender on Both - Healthgrades and RateMDs\n(blue=Female, red=Male)",x="Overall_score",y = "Density of Overall_score")+#add title and axis labels
  theme(legend.position="none")#hide the side signal of fill parameter


###### Checking  ######

boxplot(dcombine$Rating~dcombine$Years.of.Experience, # Specify the variables to graph, quantitative variable first
        col=c("orange","thistle","lightgreen","lightblue","gray","yellow"), # Specify the data set that contains the variables
        main = "Rating over Years of Experience on Healthgrades and RateMDs", #Create the chart title
        xlab = "Years of Experience",  #Create the x-axis label
        ylab = "Rating",
        las=1,  # Width of box as proportion of original
        whisklty = 1,  # Whisker line type; 1 = solid line
        staplelty = 0,  # Staple (line at end) type; 0 = none
        outpch = 16,  # Symbols for outliers; 16 = filled circle
        outcol = "slategray3", 
        notch=F,horizontal = F# Color for outliers
) #Create the y-axis label

#######Checking 

### No of years of Experience on both the Websites 

dcombine %>% #plot rating over Gender 
  ggplot(aes(x=Rating,fill=Gender))+
  geom_density(alpha=.4,position="identity")+
  labs(title = "Density of Rating over Gender spread across Years of Experience on HealthGrades and RateMDs\n(blue=Female, red=Male)",x="Rating",y = "Density of Rating")+#add title and axis labels
  theme(legend.position="none")+#hide the side signal of fill parameter
 facet_wrap(~dcombine$Years.of.Experience)



```

## Linear Regression Modeling


```{r}

library(corrplot)
library(lm.beta)
## Healthgrades 
#str(ratemdsfinal)
#str(healthgrades)

hdff1=data.frame(healthgrades[,c(3,5,20,21,22,23,24,25,26,27,28,29,30,31,32,7)])
names(hdff1)
hdff2=data.frame(healthgrades[,c(3,5,20,21,22,23,24,25,26,27,28,29,30,31,32,14)])
names(hdff2)
hdff3=data.frame(healthgrades[,c(3,5,20,21,22,23,24,25,26,27,28,29,30,31,32,17)])
names(hdff3)
hdff4=data.frame(healthgrades[,c(3,5,20,21,22,23,24,25,26,27,28,29,30,31,32,16)])
names(hdff4)
hdff5=data.frame(healthgrades[,c(3,5,20,21,22,23,24,25,26,27,28,29,30,31,32,19)])
names(hdff5)
hdff6=data.frame(healthgrades[,c(3,5,20,21,22,23,24,25,26,27,28,29,30,31,32,33)])
names(hdff6)

#Regression

lh1=lm(Rating~.,data = hdff1)
lhs1=lm.beta(lh1)


lh2=lm(Positive_Proportion~.,data = hdff2)
lhs2=lm.beta(lh2)


lh3=lm(Negative_Proportion~.,data = hdff3)
lhs3=lm.beta(lh3)


lh4=lm(Average.pos_score~.,data = hdff4)
lhs4=lm.beta(lh4)


lh5=lm(Average.neg_score~.,data = hdff5)
lhs5=lm.beta(lh5)

lh6=lm(Overall_score~.,data = hdff6)
lhs6=lm.beta(lh6)

library(stargazer)




## Corelation Plot  

str(hdff1)

corrplot(cor(hdff1[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(hdff2[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(hdff3[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(hdff4[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(hdff5[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(hdff6[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")

# RateMDs

rdff1=data.frame(ratemdsfinal[,c(3,4,17,18,19,20,21,22,23,24,25,26,27,28,32,6)])
rdff2=data.frame(ratemdsfinal[,c(3,4,17,18,19,20,21,22,23,24,25,26,27,28,32,11)])
rdff3=data.frame(ratemdsfinal[,c(3,4,17,18,19,20,21,22,23,24,25,26,27,28,32,14)])
rdff4=data.frame(ratemdsfinal[,c(3,4,17,18,19,20,21,22,23,24,25,26,27,28,32,12)])
rdff5=data.frame(ratemdsfinal[,c(3,4,17,18,19,20,21,22,23,24,25,26,27,28,32,16)])
rdff6=data.frame(ratemdsfinal[,c(3,4,17,18,19,20,21,22,23,24,25,26,27,28,32,33)])


#Correlation plots
corrplot(cor(rdff1[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(rdff2[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(rdff3[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(rdff4[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(rdff5[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(rdff6[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")

#Regression
lr1=lm(Rating~.,data = rdff1)
lrs1=lm.beta(lr1)


lr2=lm(Positive_Proportion~.,data = rdff2)
lrs2=lm.beta(lr2)


lr3=lm(Negative_Proportion~.,data = rdff3)
lrs3=lm.beta(lr3)


lr4=lm(Average.pos_score~.,data = rdff4)
lrs4=lm.beta(lr4)


lr5=lm(Average.neg_score~.,data = rdff5)
lrs5=lm.beta(lr5)

lr6=lm(Overall_score~.,data = hdff6)
lrs6=lm.beta(lr6)

lcs6

```
## Combined Linear Modeling 

```{r}

comdff1=data.frame(dcombine[,-c(17,18,19,20,21)])
comdff2=data.frame(dcombine[,-c(16,18,19,20,21)])
comdff3=data.frame(dcombine[,-c(16,17,19,20,21)])
comdff4=data.frame(dcombine[,-c(16,17,18,20,21)])
comdff5=data.frame(dcombine[,-c(16,17,18,19,21)])
comdff6=data.frame(dcombine[,-c(16,17,18,19,20)])

str(comdff6)

#Regression
lc1=lm(Rating~.,data = comdff1)
lcs1=lm.beta(lc1)


lc2=lm(Positive_Proportion~.,data = comdff2)
lcs2=lm.beta(lc2)


lc3=lm(Negative_Proportion~.,data = comdff3)
lcs3=lm.beta(lc3)


lc4=lm(Average.pos_score~.,data = comdff4)
lcs4=lm.beta(lc4)


lc5=lm(Average.neg_score~.,data = comdff5)
lcs5=lm.beta(lc5)

lc6=lm(Overall_score~.,data = comdff6)
lcs6=lm.beta(lc6)


#Correlation plots

str(comdff1)
corrplot(cor(comdff1[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(comdff2[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(comdff3[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(comdff4[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(comdff5[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")
corrplot(cor(comdff6[,-c(1:2)]),method="circle", addCoef.col="black", diag=F, type="upper")




#Stargazer

library(stargazer)
#stargazer(lh1,lh2,lh3,lh4,lh5,lh6, type="text",out = "Stargazer_healthgrades.txt")
#stargazer(lr1,lr2,lr3,lr4,lr5,lr6, type="text",out="stargazer_ratemds.txt")
#stargazer(lc1,lc2,lc3,lc4,lc5,lc6, type="text",out="stargazer_combined.txt")
stargazer(lh1,lh2,lh3,lh4,lh5,lh6, type="text", out="C:/Users/rramn/Documents/Healthcare_analytics/physician_reviews_mining/healthgrades.txt")
stargazer(lr1,lr2,lr3,lr4,lr5,lr6, type="text", out="C:/Users/rramn/Documents/Healthcare_analytics/physician_reviews_mining/ratemds.txt")
stargazer(lc1,lc2,lc3,lc4,lc5,lc6, type="text", out="C:/Users/rramn/Documents/Healthcare_analytics/physician_reviews_mining/combined.txt")


stargazer(lh1,lh2,lh3,lh4,lh5,lh6, type="text",coef=list(lhs1$standardized.coefficients,lhs2$standardized.coefficients,lhs3$standardized.coefficients,lhs4$standardized.coefficients,lhs5$standardized.coefficients,lhs6$standardized.coefficients),se=list(lh1$coefficients,lh2$coefficients,lh3$coefficients,lh4$coefficients,lh5$coefficients,lh6$coefficients),out="C:/Users/rramn/Documents/Healthcare_analytics/physician_reviews_mining/healthgrades.txt")

stargazer(lr1,lr2,lr3,lr4,lr5,lr6, type="text",coef=list(lrs1$standardized.coefficients,lrs2$standardized.coefficients,lrs3$standardized.coefficients,lrs4$standardized.coefficients,lrs5$standardized.coefficients,lrs6$standardized.coefficients),se=list(lr1$coefficients,lr2$coefficients,lr3$coefficients,lr4$coefficients,lr5$coefficients,lr6$coefficients), out="C:/Users/rramn/Documents/Healthcare_analytics/physician_reviews_mining/ratemds.txt")

stargazer(lc1,lc2,lc3,lc4,lc5,lc6, type="text",coef=list(lcs1$standardized.coefficients,lcs2$standardized.coefficients,lcs3$standardized.coefficients,lcs4$standardized.coefficients,lcs5$standardized.coefficients,lcs6$standardized.coefficients),se=list(lc1$coefficients,lc2$coefficients,lc3$coefficients,lc4$coefficients,lc5$coefficients,lc6$coefficients), out="C:/Users/rramn/Documents/Healthcare_analytics/physician_reviews_mining/combined.txt")


```








